A statistical analysis of a counterstrike game: Boston 2018

### 2025-02-26 inst/counterstrike.Rmd
consistentification
distinguish hankin2017 from hankin2017_rnw
All games played by `Cloud9`.

---
title: "A statistical analysis of a counterstrike game: Boston 2018"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: jss_hyper3.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017a.
In this short vignette I use the `hyper2` package to analyse an
influential Counter-Strike match between two professional teams (_FaZe
Clan_ and _Cloud9_) in the major championships at Boston 2018.  I use
likelihood methods to demonstrate that one player, Skadoodle, has a
legitimate claim to be the strongest player on the field; but the data
is indistinguishable from a null of equal player strength.
Counter-strike dataset kindly supplied by Zachary Hankin.

@@

>>>>

---
title: "A statistical analysis of a counterstrike game: Boston 2018"
author: "R. K. S. Hankin"
output: bookdown::html_document2
bibliography: hyper2.bib
---

@@

To cite the `hyper2` package in publications, please use @hankin2017_rmd.
In this short vignette I use the `hyper2` package to analyse an
influential Counter-Strike match between two professional teams (_FaZe
Clan_ and _Cloud9_) in the major championships at Boston 2018.  I use
likelihood methods to demonstrate that one player, Skadoodle, has a
legitimate claim to be the strongest player on the field; but the data
is indistinguishable from a null of equal player strength.
Counter-strike dataset kindly supplied by Zachary Hankin.

@@

## A red bus blue bus analysis.

I now analyse every game played by `Cloud9` in the tournament.

https://www.hltv.org/stats/teams/matches/5752/cloud9?event=3247

As far as I can tell this is every match played at ELEAGUE Major 2018  in Boston by `Cloud9`.

```{r}
a <- read.table("cloud9_boston_2018.txt",header=TRUE)
a
```

Above we see from the first line that on 28 Jan 2018, playing `FaZe` on the Inferno map we have a win, with deathorder Skadoodle, RUSH, etc.

We will look at the effect of `Skadoodle` on `Stewie2K`.

```{r}
ec <-c(autimatic=1, RUSH=1, Skadoodle=2, Stewie2K=2, tarik=1)
mk <- function(lam){
  H3 <- hyper3()
  for(i in seq_len(nrow(a))){

    d <- strsplit(a$deathorder[i],", ")[[1]]
    H3 <- H3 + cheering3(d, e=ec, help=c(1,lam))
  }
  return(H3)
}

```{r mkmaxp, cache=TRUE}
maxp(mk(0.5),give=1)
maxp(mk(1.01),give=1)
```
